D2F_exploration_fourway_and_GWAS

### 2020-06-02 R/D2F_exploration_fourway_and_gwas.Rmd
Writeup Results photoperiod cue section

```
FWCR	AP13	2921		parent - gulf
FWCR	AxD	2124		F1
FWCR	DAC	493		  parent - midwest
FWCR	VS16	1135		parent - midwest
FWCR	VxW	2242		F1
FWCR	WBC	1945		parent - gulf
FWCR	NA	4		
GWAS	AP13	4410	in FWCR also
What J #'s (if any) are DAC, VS16, WBC in the GWAS panel?
DAC J440.A, J440.B Source_ID_2 Dacotah
J230.A Source_ID_1  WBC
J292.A SOURCE_ID_1 VS16 (counted as 8X in metadata, may be an issue)

>>>>

# saveRDS(phe_all, file = "../data/all_phenotype_meas_4wcr_gwas.rds")
```
FWCR	AP13	2921		parent - gulf
FWCR	AxD	2124		F1 (AxB in results)
FWCR	DAC	493		  parent - midwest
FWCR	VS16	1135		parent - midwest
FWCR	VxW	2242		F1 (CxD in results)
FWCR	WBC	1945		parent - gulf
FWCR	NA	4		
GWAS	AP13	4410	in FWCR also
What J #'s (if any) are DAC, VS16, WBC in the GWAS panel?
DAC J440.A, J440.B Source_ID_2 Dacotah
J230.A Source_ID_1  WBC
J292.A SOURCE_ID_1 VS16 (counted as 8X in metadata, may be an issue)
